---
title: "Plots to publish"
output:
  pdf_document: 
    fig_height: 8
    fig_width: 14
  html_notebook: default
  word_document: 
    fig_height: 8
    fig_width: 14
  html_document: 
    fig_height: 8
    fig_width: 14
---


```{r}
library(ggplot2)
library(ggpubr)
library(CDM)
library(boot)
library(tidyverse)
library(stringi)
library(stringr)
library(ggridges)
library(ggrepel)
library(RColorBrewer)
library(latex2exp)
library(ggsci)
```

```{r}
rm(list = ls())
options(max.print=100)
path = "report"
#path = ""


```


```{r}
df.error.ec <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_error_ecpe.rds"))

df.error.ec.agg <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_error_agg_ecpe.rds"))

df.error.ec.fit <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_error_fit_ecpe.rds")) %>% mutate(dataset = "ECPE")

df.sim.ec.item <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_data_sim_item_ecpe.rds"))

df.error.ec.plot <- df.error.ec %>% inner_join(
  df.error.ec.agg
) %>% mutate(dataset = "ECPE")

df.error.ec.plot


```


```{r}
df.error.ti <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_error_timss.rds"))

df.error.ti.agg <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_error_agg_timss.rds"))

df.error.ti.fit <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_error_fit_timss.rds")) %>% mutate(dataset = "TIMSS")

df.sim.ti.item <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_data_sim_item_timss.rds"))

df.error.ti.plot <- df.error.ti %>% inner_join(
  df.error.ti.agg
) %>% mutate(dataset = "TIMSS")


```


```{r}
df.error.ss.u <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_error_socialscience.rds"))

df.error.ss.agg.u <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_error_agg_socialscience.rds"))

df.error.ss.fit.u <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_error_fit_socialscience.rds")) %>% mutate(dataset = "Social Psychology (Upsample)")

df.sim.ss.item <- read_rds(paste0("..\\data\\FirstYearProject\\",path,"\\df_data_sim_item_socialscience.rds"))

df.error.ss.plot.u <- df.error.ss.u %>% inner_join(
  df.error.ss.agg.u
) %>% mutate(dataset = "Social Psychology (Upsample)")

df.error.ss.plot.u


max(df.error.ss.u$attempts)

```

# Merge all Data

```{r}

breaks = c(0,10,20,40, 80, 160, 320)
labels = c(10,20,40,80, 160, 320)

#breaks = c(0,5,10,15,20,25,40, 80, 160, 320)
#labels = c(5,10,15,20,25,40,80, 160, 320)

df.error.plot <- df.error.ec.plot %>% 
  
  #bind_rows(df.error.ti.plot) %>% bind_rows(df.error.ss.plot) %>% 
  bind_rows(df.error.ti.plot) %>% bind_rows(df.error.ss.plot.u) %>% 
  
  mutate(ratio_n = as.numeric(student_question_ratio)) %>%
  
  mutate(student_question_ratio = factor(student_question_ratio, levels = sort(unique(as.numeric(student_question_ratio))), ordered = TRUE)) %>%
  
  mutate(dataset = factor(dataset, levels = c("ECPE", "TIMSS", "Social Psychology (Upsample)"))) %>% #
  
  mutate(questions = factor(questions)) %>% 
  
  group_by(dataset, group, parameter, sample_size) %>%
  
    mutate(question_n = n(), qsr = round(n()/sample_size)) %>% 
  ungroup() %>%
  
  mutate(attempts = round(attempts)) %>% 
  
  #Average attempts between partitions for each question.
  
  group_by(dataset, parameter, questions, student_question_ratio) %>%
    mutate(attempts_disc_n = round(mean(attempts))) %>% ungroup() %>%
    mutate(attempts_disc = cut(attempts_disc_n, 
                          breaks = c(breaks, max(.$attempts)),
                          labels = c(labels, "320+"),
                          #breaks = c(0,10,20,40, 80, 160, 320, max(.$attempts)),
                          #labels = c(10,20,40,80, 160, 320, "320+"),
                          #breaks = c(0,5, 10,15,20,25,30,35, max(.$attempts)),
                          #labels = c(5, 10,15,20,25,30,35,"35+"),
                          include.lowest = TRUE, right = TRUE, ordered_result = TRUE))  %>%
    
    
ungroup() %>%
  # Adding upsample column to represent attempts that were generated due to non-parameteric bootstrap upsampling
  mutate(upsampled = case_when(
    #(dataset == "TIMSS" & attempts > 400)  ~ "Upsampled IAC", #ratio_n > 21
    #(dataset == "Social Psychology (Upsample)")  ~ "Upsampled Dataset", #ratio_n > 0.5  & attempts > 15
    TRUE ~ "Original Dataset"
    
    
  )) %>%
  
  
  #mutate(sampling_error = sampling_error / sqrt(1000)) %>% # To get Smulation Error
  
  # Average avg_attempts between partitions aggregated over all questions.
  
  group_by(dataset, parameter, attempts) %>%
  mutate(avg_attempts = round(mean(avg_attempts))) %>%
  
  ungroup() %>%
  arrange(dataset, group, parameter, sample_size)

df.error.plot <- df.error.plot %>% mutate(qsr = factor(qsr, ordered = TRUE), 
                                          sample_size = factor(sample_size, ordered = TRUE), 
                                          avg_attempts = factor(avg_attempts, ordered = TRUE)
                                          )
distinct(df.error.plot, dataset, upsampled, student_question_ratio, attempts_disc_n) 

summary(df.error.plot$attempts)



df.error.plot.ss <- df.error.plot %>% filter(dataset == "Social Psychology (Upsample)") %>% filter(sample_size == 525) %>% ## Get Full data, no sample sizes
  mutate(attempts_disc = cut(attempts,breaks = c(0,5,10,max(.$attempts)), labels = c("5", "10", "10+")))


#df.error.plot %>% filter(dataset == "Social Psychology (Upsample)") %>% select(sample_size) %>% distinct()
```

```{r}

df.fit.plot <- df.error.ec.fit %>% bind_rows(df.error.ti.fit) %>% bind_rows(df.error.ss.fit.u)
#df.fit.plot

```


# Sampling Error



```{r}

df.error.plot %>% select(parameter, group, questions, sampling_mean, attempts_disc, student_question_ratio, dataset) %>% 
  spread(key="group", value = "sampling_mean") %>% arrange(attempts_disc) %>% #filter(parameter == "Guess") %>%
  
  
  
  ggplot() + 
  aes(x=`Partition 1`, y=`Partition 2`, color = parameter) +
  geom_point(show.legend = TRUE, alpha = 0.4) +
  facet_grid(dataset+parameter~attempts_disc, scales = "free") + 
  ggtitle("Distribution of Sampling Mean for each Sample Size") + 
  #scale_x_continuous(breaks = c(0,0.5)) + 
  #scale_y_continuous(breaks = c(0,0.5)) + 
  ggpubr::theme_pubclean() + 
  labs(color = "", subtitle = "IAC") + 
  theme(legend.position = "bottom")

```


Simulation count, this differs because in case of missing data, each item may not be attempted in each simulation batch.
# Bayesian MAB
```{r}

df.mean_diff <- df.error.plot  %>% select(parameter, group, questions, sampling_mean, student_question_ratio, attempts_disc, dataset, upsampled, total_count) %>% 
  spread(key="group", value = "sampling_mean") %>% rename("Partition1_mean" = `Partition 1`, "Partition2_mean" = `Partition 2`)  %>% 
  
  group_by(dataset,parameter,student_question_ratio,questions) %>% 
  mutate(abs_bias = abs(Partition1_mean - Partition2_mean)) %>%
  ungroup()
  


df.mean_diff.ss <- df.error.plot.ss  %>% select(parameter, group, questions, attempts_disc, sampling_mean, total_count) %>% 
  spread(key="group", value = "sampling_mean") %>% rename("Partition1_mean" = `Partition 1`, "Partition2_mean" = `Partition 2`)  %>% 
  
  group_by(parameter,questions, attempts_disc) %>% 
  mutate(abs_bias = abs(Partition1_mean - Partition2_mean)) %>%
  ungroup()


#df.error_diff <- df.error.plot  %>% select(parameter, group, questions, sampling_error, student_question_ratio, attempts_disc_n, dataset, upsampled, total_count) %>% 
#  spread(key="group", value = "sampling_error") %>% rename("Partition1_error" = `Partition 1`, "Partition2_error" = `Partition 2`)  %>% 
  
#  group_by(dataset,parameter,student_question_ratio,questions) %>% 
#  mutate(error_diff = Partition1_error - Partition2_error)  

#df.error.plot %>% group_by(dataset,total_count) %>% tally()


```

```{r}
#df.mean_diff %>% group_by(dataset, parameter) %>% top_n(1, wt = Partition1_mean)
```



# Mean over all items
```{r}

#df.diff <- df.mean_diff %>% group_by(dataset, parameter, attempts_disc_n,upsampled) %>% #,attempts, student_question_ratio
#  summarize(
#    mn = mean(abs_bias),
#    sd = sd(abs_bias),
#    min = min(abs_bias),
#    max = max(abs_bias),
#    var = var(abs_bias)
    
#  )

#df.diff

```


# Plot for poster presentation

```{r}

df.t <- df.mean_diff %>% filter(dataset == "ECPE") 

#df.t$attempts_disc <- recode(df.t$attempts_disc, "400" = "[300,1461]", "800" = "[300,1461]", "1200+" = "[300,1461]")

df.t %>%

  
  ggplot() + 
  aes(x= attempts_disc, y = abs_bias, fill = paste(parameter, "Parameter")) +
  
  #geom_point(size = 3) +
  geom_boxplot(alpha = 0.6, show.legend = FALSE) +
 
  facet_grid(parameter~.) +
  labs(x="Item Administered Count (IAC)", y = "Bayesian-MAB", fill = "") + 
  theme_pubclean() + theme(legend.position = "bottom", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10),
                           
                           #panel.border = element_rect(colour = "black", fill=NA, size=1),
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  #scale_fill_brewer(palette="Set2") + 
  scale_fill_manual(values = c("#E46F1F", "#7AC043"))   + 
  #stat_summary(geom = "text", fun.data = n_fun) +
  scale_y_continuous(breaks = seq(0,0.2,0.02))

  #ggsave("EC_g.png", dpi = "retina", width = 15, height = 6, units = "in") 

```



```{r}

df.t <- df.mean_diff %>% filter(dataset == "TIMSS") 


#df.t$attempts_disc <- recode(df.t$attempts_disc, "400" = "300")

df.t %>%

  
  ggplot() + 
  aes(x= attempts_disc, y = abs_bias, fill = paste(parameter, "Parameter")) +
  
  #geom_point(size = 3) +
  geom_boxplot(alpha = 0.6, show.legend = FALSE) +
 
  facet_grid(parameter~.) +
  labs(x="Item Administered Count (IAC)", y = "Bayesian-MAB", fill = "") + 
  theme_pubclean() + theme(legend.position = "bottom", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10),
                           
                           #panel.border = element_rect(colour = "black", fill=NA, size=2, linetype = "dotted"),
                           #strip.background = element_rect(fill = "White", colour = "Black")
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  #scale_fill_brewer(palette="Set2") + 
  scale_fill_manual(values = c("#E46F1F", "#7AC043"))  + 
  scale_y_continuous(breaks = seq(0,0.2,0.02))
  

  #ggsave("TI_g.png", dpi = "retina", width = 15, height = 6, units = "in") 

```



```{r}

df.mean_diff.ss %>% 

  
  ggplot() + 
  aes(x = attempts_disc, y= abs_bias) + #, color = paste(parameter, "Parameter")) +
  
  geom_jitter(width = 0.1, alpha = 0.15) +
  #geom_boxplot(alpha = 0.6, show.legend = FALSE) +
  #geom_histogram()+
  #stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "lightBlue", size = 0.8) + 
  facet_grid(parameter~., scales = "free") +
  labs(x="Item Administered Count (IAC)", y = "Bayesian-MAB", fill = "", color = "") + 
  theme_pubclean() + theme(legend.position = "bottom", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10),
                           
                           #panel.border = element_rect(colour = "black", fill=NA, size=2, linetype = "dotted"),
                           #strip.background = element_rect(fill = "White", colour = "Black")
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) 

  
  

  #ggsave("combined_b_mab_ss.png", dpi = "retina", width = 7.5, height = 4, units = "in") 

```


```{r}

df.mean_diff %>% filter(dataset != "Social Psychology (Upsample)") %>%

  
  ggplot() + 
  aes(x= attempts_disc, y = abs_bias) + #, color = paste(parameter, "Parameter")) +
  
  geom_jitter(width = 0.1, alpha = 0.15) +
  #geom_boxplot(alpha = 0.6, show.legend = FALSE) +
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "lightBlue", size = 0.8) + 
  facet_grid(parameter~dataset, scales = "free") +
  labs(x="Item Administered Count (IAC)", y = "Bayesian-MAB", fill = "", color = "") + 
  theme_pubclean() + theme(legend.position = "bottom", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10),
                           
                           #panel.border = element_rect(colour = "black", fill=NA, size=2, linetype = "dotted"),
                           #strip.background = element_rect(fill = "White", colour = "Black")
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  #scale_fill_brewer(palette="Set2") + 
  scale_fill_manual(values = c("#E46F1F", "#7AC043"))  + 
  scale_y_continuous(limits = c(0,0.12), breaks = seq(0,0.12,0.02))
  

  ggsave("combined_b_mab.png", dpi = "retina", width = 7.5, height = 3, units = "in") 

```




## Individual Differences


```{r}
df.ind_z.ec <- df.sim.ec.item %>% #filter(str_detect(questions,"E1$|E2$|E3$|E4$")) %>% 
  mutate(attempts_disc = cut(attempts, 
                          breaks = c(breaks, max(.$attempts)),
                          labels = c(labels, "320+"),
                          #breaks = c(0,10,20,40, 80, 160, 320, max(.$attempts)),
                          #labels = c(10,20,40,80, 160, 320, "320+"),
                          include.lowest = TRUE, right = TRUE, ordered_result = TRUE)) %>% 
           
           
           #cut(attempts, 
                        #     breaks = c(seq(min(.$attempts), 100, 10), seq(100, max(.$attempts), 100), max(.$attempts)), 
                         #    labels = c(seq(min(.$attempts), 100, 10), seq(100, max(.$attempts), 100), max(.$attempts))[-1],
                        #     dig.lab = 5,
                        #     right = TRUE, include.lowest = TRUE, ordered_result = TRUE)) %>%
  select(-attempts)  %>% 
  spread(key = group, value = item_parameters) %>% #write_excel_csv("../data/FirstYearProject/individual_z.csv")
  
  group_by(parameter, questions, attempts_disc, sim_no) %>%
  
  mutate(d = `Partition 1` - `Partition 2`,
         d_abs = abs(`Partition 1` - `Partition 2`)
         ) %>%
  
  group_by(parameter, questions, attempts_disc) %>%
  
  summarise(Mean = mean(d),
            MAB = mean(d_abs),
            `Standard Deviation` = sd(d), # This is sample standard deviation
            #Z = Mean/(`Standard Deviation` + 0.00001),
            #cor_coef = cor(`Partition 1` , `Partition 2`, use = "pairwise.complete.obs", method = "kendall"),
            #var_coef = `Standard Deviation`/abs(Mean)
         ) %>% ungroup() %>%
  #mutate(is_invariant = ifelse(Mean <= 0.1 & `Standard Deviation` <= 0.1, TRUE, FALSE))
  mutate(is_invariant = ifelse(MAB < 0.1, TRUE, FALSE))
  

df.ind_z.ti <- df.sim.ti.item %>%
  #filter(questions == "M051305", sample_size == 1010) %>% 
  mutate(attempts_disc = cut(attempts, 
                          breaks = c(breaks, max(.$attempts)),
                          labels = c(labels, "320+"),
                          #breaks = c(0,10,20,40, 80, 160, 320, max(.$attempts)),
                          #labels = c(10,20,40,80, 160, 320, "320+"),
                          include.lowest = TRUE, right = TRUE, ordered_result = TRUE)) %>% 
           
                          #                 cut(attempts, 
                          #                 breaks = c(seq(min(.$attempts), 100, 10), seq(100, max(.$attempts), 100), max(.$attempts)), 
                          #                 labels = c(seq(min(.$attempts), 100, 10), seq(100, max(.$attempts), 100), max(.$attempts))[-1],
                          #                 right = TRUE, include.lowest = TRUE)) 

  
  select(-attempts)  %>% 
  spread(key = group, value = item_parameters) %>% 
  
  group_by(parameter, questions, attempts_disc, sim_no) %>% 
  #group_by(sim_no, sample_size, parameter, student_question_ratio, questions, attempts_disc) %>%
  
  mutate(d = `Partition 1` - `Partition 2`,
         d_abs = abs(`Partition 1` - `Partition 2`)
         ) %>% 
  na.omit() %>% # To remove the cases where item couldn't find same attempt count (discrete) for same simulation and same sample size
  
  group_by(parameter, questions, attempts_disc) %>%
  
  summarise(Mean = mean(d),
            MAB = mean(d_abs),
            `Standard Deviation` = sd(d), # This is sample standard deviation
            #Z = Mean/(`Standard Deviation` + 0.00001),
            #cor_coef = cor(`Partition 1` , `Partition 2`, use = "pairwise.complete.obs", method = "kendall"),
            #var_coef = `Standard Deviation`/abs(Mean)
         ) %>% ungroup() %>%
  #mutate(is_invariant = ifelse(Mean <= 0.1 & `Standard Deviation` <= 0.1, TRUE, FALSE))
  mutate(is_invariant = ifelse(MAB < 0.1, TRUE, FALSE))
```

Treating Social Psychology dataset separately 
```{r}
df.ind_z.ss <- df.sim.ss.item %>% filter(sample_size == 525) %>%  # getting whole dataset. No samples.
  mutate(attempts_disc = cut(attempts,breaks = c(0,5,10,max(.$attempts)), labels = c("5", "10", "10+"))) %>%
  spread(key = group, value = item_parameters) %>% 
  group_by(parameter, questions, attempts_disc, sim_no) %>% 
  #group_by(sim_no, sample_size, parameter, student_question_ratio, questions, attempts_disc) %>%
  
  mutate(d = `Partition 1` - `Partition 2`,
         d_abs = abs(`Partition 1` - `Partition 2`)
         ) %>% 
  na.omit() %>% # To remove the cases where item couldn't find same attempt count (discrete) for same simulation and same sample size
  
  group_by(parameter, questions, attempts_disc) %>%
  
  summarise(Mean = mean(d),
            MAB = mean(d_abs),
            `Standard Deviation` = sd(d), # This is sample standard deviation
            #Z = Mean/(`Standard Deviation` + 0.00001),
            #cor_coef = cor(`Partition 1` , `Partition 2`, use = "pairwise.complete.obs", method = "kendall"),
            #var_coef = `Standard Deviation`/abs(Mean)
         ) %>% ungroup() %>%
  #mutate(is_invariant = ifelse(Mean <= 0.1 & `Standard Deviation` <= 0.1, TRUE, FALSE))
  mutate(is_invariant = ifelse(MAB < 0.1, TRUE, FALSE))
  

#df.ind_z <- df.ind_z.ec %>% bind_rows(df.ind_z.ti) %>% bind_rows(df.ind_z.ss) #%>% mutate(attempts_disc = factor(attempts_disc))

#df.ind_z

```



```{r}

#rgb(228,111,31, maxColorValue = 255)
#rgb(122,192,67, maxColorValue = 255)

df.t <- df.ind_z.ec #%>% #write_excel_csv("../data/FirstYearProject/individual_z.csv")
#df.t$attempts_disc <- recode(df.t$attempts_disc, "400" = "[300,1461]", "500" = "[300,1461]", "700" = "[300,1461]", "1400" = "[300,1461]", "1461" = "[300,1461]")

df.t %>%
  
  ggplot() + 
  aes(x=attempts_disc, y = MAB, fill = paste(parameter, "Parameter")) + 
  #geom_jitter(width = 0.1, alpha = 0.15) + 
  geom_boxplot(alpha = 0.6, show.legend = FALSE) + 
  facet_grid(parameter~.) + 
  labs(x="Item Administered Count (IAC)", y = "MAB", fill = "") +
  theme_pubclean() + theme(legend.position = "bottom", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10),
                           
                           #panel.border = element_rect(colour = "black", fill=NA, size=1),
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  #scale_fill_brewer(palette="Set2") + 
  scale_fill_manual(values = c("#E46F1F", "#7AC043")) + 
  scale_y_continuous(breaks = seq(0,0.6,0.05)) # limits = c(0,0.5), breaks = c(0.2, 0.4)

  #ggsave("EC.png", dpi = "retina", width = 15, height = 6, units = "in") 


```


```{r}

df.ind_z.ti %>% #write_excel_csv("../data/FirstYearProject/individual_z.csv")
 ggplot() + 
  aes(x=attempts_disc, y = MAB, fill = paste(parameter, "Parameter")) + 
  #geom_jitter(width = 0.1, alpha = 0.15) + 
  geom_boxplot(alpha = 0.6, show.legend = FALSE) + 
  facet_grid(parameter~.) +
  labs(x="Item Administered Count (IAC)", y = "MAB", fill = "") + 
  theme_pubclean()+ theme(legend.position = "bottom", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10)
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  #scale_fill_brewer(palette="Set2") + 
  scale_fill_manual(values = c("#E46F1F", "#7AC043")) + 
  scale_y_continuous(breaks = seq(0,0.6,0.1))

  #ggsave("TI.png", dpi = "retina", width = 15, height = 6, units = "in") 


```

```{r}
df.ind_z.ss %>% 
  ggplot() + 
  aes(x=attempts_disc, y=MAB) + 
  geom_jitter()
  
```



```{r}

df.ind_z.ti %>% mutate(dataset="TIMSS") %>% 
   bind_rows(
    df.ind_z.ec %>% mutate(dataset="ECPE")
) %>%
  
 ggplot() + 
  aes(x=attempts_disc, y = MAB) + #, color = paste(parameter, "Parameter")) + 
  geom_jitter(width = 0.1, alpha = 0.15) + 
  #geom_boxplot(alpha = 0.6, show.legend = FALSE) + 
  facet_grid(parameter~dataset, scales = "free") +
  labs(x="Item Administered Count (IAC)", y = "MAB", fill = "", color = "") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "lightBlue", size = 0.8) + 
  theme_pubclean()+ theme(legend.position = "bottom", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10)
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  #scale_fill_brewer(palette="Set2") + 
  scale_fill_manual(values = c("#E46F1F", "#7AC043")) + 
  scale_y_continuous(breaks = seq(0,0.6,0.1))

  ggsave("combined_mab.png", dpi = "retina", width = 7.5, height = 3, units = "in") 


```



```{r}


df.mean_diff %>% filter(dataset == "ECPE") %>% select(parameter, attempts_disc, abs_bias) %>% rename(metric = abs_bias) %>% mutate(type = "Bayesian-MAB") %>% bind_rows(
  
  df.ind_z.ec %>% select(parameter, attempts_disc, MAB) %>% rename(metric = MAB) %>% mutate(type = "MAB")
) %>%
  
  mutate(type = factor(type, levels = c("MAB", "Bayesian-MAB"), ordered = TRUE)) %>% 
  ggplot() + 
  aes(x=attempts_disc, y=metric) + 
  geom_jitter(width = 0.1, alpha = 0.15) + 
  facet_grid(parameter~type) + 
  labs(x="Item Administered Count (IAC)", y = "", fill = "", color = "") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "lightBlue", size = 0.8)  + 
  theme_pubclean()+ theme(legend.position = "bottom", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10)
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) #+ 
  #scale_y_continuous(breaks = c(0,0.5,0.1,0.2,0.3,0.4))

 ggsave("ecpe_mab_bmab.png", dpi = "retina", width = 7.5, height = 3, units = "in")

```


```{r}


df.mean_diff %>% filter(dataset == "TIMSS") %>% select(parameter, attempts_disc, abs_bias) %>% rename(metric = abs_bias) %>% mutate(type = "Bayesian-MAB") %>% bind_rows(
  
  df.ind_z.ti %>% select(parameter, attempts_disc, MAB) %>% rename(metric = MAB) %>% mutate(type = "MAB")
) %>%
  
  mutate(type = factor(type, levels = c("MAB", "Bayesian-MAB"), ordered = TRUE)) %>% 
  ggplot() + 
  aes(x=attempts_disc, y=metric) + 
  geom_jitter(width = 0.1, alpha = 0.15) + 
  facet_grid(parameter~type) + 
  labs(x="Item Administered Count (IAC)", y = "", fill = "", color = "") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "lightBlue", size = 0.8)  + 
  theme_pubclean()+ theme(legend.position = "bottom", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10)
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) #+ 
  #scale_y_continuous(breaks = c(0,0.5,0.1,0.2,0.3,0.4))

 ggsave("timss_mab_bmab.png", dpi = "retina", width = 7.5, height = 3, units = "in")

```


```{r}

df.mean_diff.ss %>% select(parameter, abs_bias) %>% rename(metric = abs_bias) %>% mutate(metric_type = "Bayesian-MAB") %>% bind_rows( 
df.ind_z.ss %>% select(parameter, MAB) %>% rename(metric = MAB) %>% mutate(metric_type = "MAB")
) %>%
  
  ggplot() + 
  aes(x=metric, fill = metric_type) + 
  geom_histogram() + 
  facet_grid(parameter~metric_type, scales = "free")

```


```{r}

df.mean_diff.ss %>% select(parameter, abs_bias, attempts_disc) %>% rename(metric = abs_bias) %>% mutate(metric_type = "Bayesian-MAB") %>% bind_rows( 
df.ind_z.ss %>% select(parameter, MAB, attempts_disc) %>% rename(metric = MAB) %>% mutate(metric_type = "MAB")
) %>% mutate(metric_type = factor(metric_type, levels = c("MAB", "Bayesian-MAB"), ordered = TRUE)) %>% filter(attempts_disc != 5) %>%
  
  ggplot() + 
  aes(x=attempts_disc, y = metric, shape = attempts_disc, color = attempts_disc) + 
  geom_jitter(width = 0.1, alpha = 0.05) + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "lightBlue", size = 0.8, show.legend = FALSE) + 
  facet_grid(parameter~metric_type, scales = "free") + 
  theme_pubclean()+ theme(legend.position = "right", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10)
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
  labs(x="", y="" , shape = "IAC", color = "IAC", size = "IAC", alpha = "IAC") + 
  #scale_color_manual(values = c("black", "#E46F1F")) + 
  #scale_size_manual(values = c(2,3)) + 
  scale_color_uchicago(palette = "dark")


 ggsave("combined_ss.png", dpi = "retina", width = 7.5, height = 3, units = "in") 

```

```{r}

df.plot.ss <- df.mean_diff.ss %>% select(parameter, abs_bias, attempts_disc) %>% rename(metric = abs_bias) %>% mutate(metric_type = "Bayesian-MAB") %>% bind_rows( 
df.ind_z.ss %>% select(parameter, MAB, attempts_disc) %>% rename(metric = MAB) %>% mutate(metric_type = "MAB")
) %>% mutate(metric_type = factor(metric_type, levels = c("MAB", "Bayesian-MAB"), ordered = TRUE))

df.plot.ss %>%
  
  ggplot() + 
  aes(x=attempts_disc, y = metric) + 
  geom_jitter(width = 0.1, alpha = 0.15) + 
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "lightBlue", size = 0.8, show.legend = FALSE) + 
  facet_grid(parameter~metric_type, scales = "free") + 
  theme_pubclean()+ theme(legend.position = "right", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10)
                           
                           ) + guides(colour = guide_legend(override.aes = list(alpha = 1))) + 
  labs(x="Item Administered Count (IAC)", y="" , shape = "IAC", color = "IAC", size = "IAC", alpha = "IAC") #+ 
  #scale_color_manual(values = c("black", "#E46F1F")) + 
  #scale_size_manual(values = c(2,3)) + 
  #scale_color_uchicago(palette = "dark")


 ggsave("combined_ss.png", dpi = "retina", width = 7.5, height = 3, units = "in") 

```

```{r}

df.plot.ss.comp <- df.plot.ss %>% filter(attempts_disc == 10) %>% group_by(parameter, attempts_disc, metric_type) %>% summarise(central_value = mean(metric, na.rm = TRUE), sd = sd(metric, na.rm = TRUE)) %>% mutate(dataset = "SP_UTD") %>% rename(type = metric_type)
df.plot.ss.comp
```


# Comparing everything

```{r}
df.t <- 
  df.mean_diff %>% filter(dataset == "ECPE") %>% select(parameter, attempts_disc, abs_bias) %>% group_by(parameter,attempts_disc) %>% summarise(central_value = mean(abs_bias), sd = sd(abs_bias)) %>% ungroup() %>% mutate(dataset = "ECPE", type = "Bayesian-MAB") %>%
  
  bind_rows(
    df.mean_diff %>% filter(dataset == "TIMSS") %>% select(parameter, attempts_disc, abs_bias) %>% group_by(parameter,attempts_disc) %>% summarise(central_value = mean(abs_bias), sd = sd(abs_bias)) %>% ungroup() %>% mutate(dataset = "TIMSS", type = "Bayesian-MAB")
) %>% bind_rows(
  
  df.ind_z.ec %>% select(parameter, attempts_disc, MAB) %>% group_by(parameter,attempts_disc) %>% summarise(central_value = median(MAB), sd = sd(MAB)) %>% ungroup() %>% mutate(dataset = "ECPE", type = "MAB")
) %>% bind_rows(
  
  df.ind_z.ti %>% select(parameter, attempts_disc, MAB) %>% group_by(parameter,attempts_disc) %>% summarise(central_value = median(MAB), sd = sd(MAB)) %>% ungroup() %>% mutate(dataset = "TIMSS", type = "MAB")
) %>%
  
  mutate(type = factor(type, levels = c("MAB", "Bayesian-MAB"), ordered = TRUE))

df.t
```


```{r}

ggplot() + 
  
  
   
  geom_line(data = df.t %>% filter(type == "MAB"), 
            aes( x=attempts_disc, y=central_value, 
                 color = paste0(dataset), 
                 group = paste0(dataset),
                 #linetype = paste0(dataset)
                 ),
            size = 1
            ) + 
  geom_errorbar(data = df.t %>% filter(type == "MAB"), 
                aes(x=attempts_disc, 
                    ymin = central_value - sd, 
                    ymax = central_value + sd, 
                    color = paste0(dataset),
                    #linetype = paste0(dataset)
                    ), 
                width = 0.25, size = 0.9,linetype = "solid",
                position = position_dodge(width = 0.25)) + 

  
  
  geom_line(data = df.t %>% filter(type == "Bayesian-MAB"), 
            aes( x=attempts_disc, y=central_value, 
                 color = paste0(dataset), 
                 group = paste0(dataset),
                 #linetype = paste0(dataset)
                 ),
            size = 1
            ) + 
  geom_errorbar(data = df.t %>% filter(type == "Bayesian-MAB"), 
                aes(x=attempts_disc, 
                    ymin = central_value - sd, 
                    ymax = central_value + sd,
                    color = paste0(dataset),
                    #linetype = paste0(dataset)
                    ), 
                width = 0.25, size = 0.9,linetype = "solid",
                position = position_dodge(width = 0.25)) + 
  
  
  geom_point(data=df.plot.ss.comp, 
                  aes(x=attempts_disc, 
                      y=central_value,
                      fill = dataset),
                  size = 4, alpha = 0.5
                ) + 
   
  
  facet_grid(parameter~type) + 
  labs(color = "", linetype = "", fill = "Datasets") + 
  theme_pubclean() + 
  labs(x="Item Administered Count (IAC)", y = "Mean/Standard Deviation") + 
  scale_color_uchicago() + theme(legend.position = "right", 
                           axis.text=element_text(size=10),
                           legend.text = element_text(size = 10),
                           
                           strip.text = element_text(size = 10),
                           axis.title=element_text(size=10)
                           
                           ) + 
  scale_y_continuous(breaks = c(0,0.05,0.1,0.2,0.3,0.4))


ggsave("all_combined.png", dpi = "retina", width = 7.5, height = 3, units = "in") 

```


# EDA Model Fit

Need to take average because for different sample sizes there can be same number of attempts

```{r}

#df.fit.plot.attempts <- df.fit.plot %>% group_by(group, parameter, fit, dataset, sample_size) %>% summarise_all(.funs = mean)
#df.fit.plot.attempts
```


```{r}
df.fit.plot %>% arrange(attempts) %>% 
  mutate(attempts_bin = cut(round(attempts), 
                            breaks = c(seq(min(.$attempts), 100, 50), seq(100, max(.$attempts), 100), max(.$attempts)), 
                            labels = c(seq(1, 100, 50), seq(100, max(.$attempts), 100), max(.$attempts))[-1], 
                            ordered_result = TRUE)) %>% 
  
  filter(parameter == "SRMSR") %>%
  ggplot() + 
  aes(x=sample_size, y=sampling_mean) + 
  geom_point() + 
  facet_grid(dataset~group, scales = "free") #+ 
  #scale_y_continuous(breaks = seq(0,0.5,0.05))
  
```





