---
title: "CDM Pilot Study for TIMSS"
output: html_notebook
---


```{r}
library(ggplot2)
library(ggpubr)
library(CDM)
library(boot)
library(tidyverse)
library(stringi)
library(stringr)
```

# Read Data
```{r}
rm(list = ls())
source('calculate_parameters.R')
options(max.print=100)


Q <- data.timss11.G4.AUT.part$q.matrix1
X <- data.timss11.G4.AUT.part$data[,paste(Q$item)]
Q <- Q[,-1]


```

```{r}
X 
```

```{r }
Q
```

# Summary of Attempts

## Items administered 
```{r}

summary(colSums(!is.na(X[1:56,])))

```

## Questions shown to each student

```{r}

X %>% mutate(na_per_row = rowSums(is.na(.[1:47]))) %>% group_by(na_per_row) %>% tally()


```


# Student to Item Ratio

```{r}

dim(X)[1] / dim(X)[2]

```

# Missing Responses
## Total missing
```{r}
sum(is.na(X))
```

## Total Data
```{r}
(dim(X)[1] * dim(X)[2])
```

## Percentage missing
```{r}
percent_na <- round((sum(is.na(X)) / (dim(X)[1] * dim(X)[2])) * 100,2)
percent_na
```


# Student Performance


# Bootstrap Sample 

Boot requires a custom function that would return row wise stats. In case of dataframe, each row is considered as a multi-variate observation. First parameter of the custom function takes the data input and second parameter takes the importance of data given current bootstrap iteration. stype defines second parameter.



```{r}



#X <- as.data.frame(X) 
#Q <- as.data.frame(Q) 




#model_dina <- gdina(data =  data.ecpe$data[,-1] , q.matrix =  data.ecpe$q.matrix, maxit = 10, rule = "GDINA2")

model_dina <- din(data = X, q.matrix =  Q, progress = FALSE)

```



# Calculate item parameters

```{r}
# Let's suffle X
#X <- X %>% sample_frac(1)

#Divide X to 2 parts
#X.p1 <- X %>% head(round(dim(X)[1]/2))
#X.p2 <- X %>% tail(round(dim(X)[1]/2))


```



```{r message=FALSE, warning=FALSE}

sample_sizes <- get_sample_sizes(dim(X)[1], dim(X)[2])


colSums(!is.na(X)) 


df.t <- get_mean_sample_error(X, Q, sample_sizes[1])

df.error <- df.t[[1]]
df.error.agg <- df.t[[2]]
df.error.fit <- df.t[[3]]
df.data.sim.item <- df.t[[4]]

```


```{r message=FALSE, warning=FALSE}

for(i in 2:length(sample_sizes)) {
  
  df.t <- get_mean_sample_error(X, Q, sample_sizes[i])
  
  df.error.t <- df.t[[1]]
  df.error.agg.t <- df.t[[2]]
  df.error.fit.t <- df.t[[3]]
  df.data.sim.item.t <- df.t[[4]]
  
  df.error <- df.error %>% union(
    
    df.error.t
  )
  
  df.error.agg <- df.error.agg %>% union(
    
    df.error.agg.t
  )

  df.error.fit <- df.error.fit %>% union(
    
    df.error.fit.t
  )  
  
  df.data.sim.item <- df.data.sim.item %>% union(
  
  df.data.sim.item.t
  )
  
}

#debugonce(get_mean_sample_error)

```

```{r}
write_rds(df.error, "..\\data\\measurement_invariance\\df_error_timss.rds")

write_rds(df.error.agg, "..\\data\\measurement_invariance\\df_error_agg_timss.rds")

write_rds(df.error.fit, "..\\data\\measurement_invariance\\df_error_fit_timss.rds")

write_rds(df.data.sim.item, "..\\data\\measurement_invariance\\df_data_sim_item_timss.rds")

```
