---
title: "CDM Pilot Study for Social Science"
output: html_notebook
---


```{r}
library(ggplot2)
library(ggpubr)
library(CDM)
library(boot)
library(tidyverse)
library(stringi)
library(stringr)
```

# Read Data
```{r}
rm(list = ls())
source('calculate_parameters.R')
options(max.print=100)


df.X <- read_csv("C:\\Users\\rkm160630\\OneDrive - The University of Texas at Dallas\\Ritesh Folder\\PhD\\FirstYearProject\\data\\X.csv") %>% mutate_all(as.integer)
df.Q <- read_csv("C:\\Users\\rkm160630\\OneDrive - The University of Texas at Dallas\\Ritesh Folder\\PhD\\FirstYearProject\\data\\Q.csv") %>% mutate_all(as.integer)


X = df.X %>% select(-SubjectID, -File) %>% rename_all(function(x) paste0("Q",x))
Q = df.Q %>% select(-Q_UNIQUE_ID) %>% rename_all(function(x) paste0("S",x))
X <- as.data.frame(X) 
Q <- as.data.frame(Q) 

#X = data.ecpe$data %>% select(-id)
#Q = data.ecpe$q.matrix

#Q <- data.timss11.G4.AUT.part$q.matrix1
#X <- data.timss11.G4.AUT.part$data[,paste(Q$item)]
#Q <- Q[,-1]


```

```{r}
X 
```

```{r }
Q
```

```{r}
#n=dim(X)[1]
#X <- X %>% sample_n(size = n, replace = FALSE)
```

```{r}
percent_na <- round((sum(is.na(X)) / (dim(X)[1] * dim(X)[2])) * 100,2)
percent_na
```


# Student Performance


# Bootstrap Sample 

Boot requires a custom function that would return row wise stats. In case of dataframe, each row is considered as a multi-variate observation. First parameter of the custom function takes the data input and second parameter takes the importance of data given current bootstrap iteration. stype defines second parameter.



```{r}



#X <- as.data.frame(X) 
#Q <- as.data.frame(Q) 




#model_dina <- gdina(data =  data.ecpe$data[,-1] , q.matrix =  data.ecpe$q.matrix, maxit = 10, rule = "GDINA2")

model_dina <- din(data = X, q.matrix =  Q, progress = FALSE)

```



# Calculate item parameters

```{r}
# Let's suffle X
X <- X %>% sample_frac(1)

#Divide X to 2 parts
X.p1 <- X %>% head(round(dim(X)[1]/2))
X.p2 <- X %>% tail(round(dim(X)[1]/2))


```

```{r}

t_cdm <- total_cdm_fn(X)

t_cdm[1,]

```


```{r}

#df.t <- get_sample_sizes(dim(X.p1)[1], dim(X.p1)[2])
df.t <- get_sample_sizes(dim(X.p1)[1] , dim(X.p1)[2]) #+ dim(X.p2)[1]

student_question_ratios <- df.t[[1]]
sample_sizes <- df.t[[2]]

df.t <- get_mean_sample_error(X.p1, X.p2, sample_sizes[1], student_question_ratios[1],2)

df.error <- df.t[[1]]
df.error.agg <- df.t[[2]]

```


```{r}

for(i in 2:length(sample_sizes)) {
  
  df.t <- get_mean_sample_error(X.p1, X.p2, sample_sizes[i], student_question_ratios[i],2)
  
  df.error.t <- df.t[[1]]
  df.error.agg.t <- df.t[[2]]

  df.error <- df.error %>% union(
    
    df.error.t
  )
  
  df.error.agg <- df.error.agg %>% union(
    
    df.error.agg.t
  )
  
}

#debugonce(get_mean_sample_error)

```

```{r}

write_rds(df.error, "C:\\Users\\rkm160630\\OneDrive - The University of Texas at Dallas\\Ritesh Folder\\PhD\\FirstYearProject\\data\\df_error_socialscience.rds")

write_rds(df.error.agg, "C:\\Users\\rkm160630\\OneDrive - The University of Texas at Dallas\\Ritesh Folder\\PhD\\FirstYearProject\\data\\df_error_agg_socialscience.rds")

df.error <- read_rds("C:\\Users\\rkm160630\\OneDrive - The University of Texas at Dallas\\Ritesh Folder\\PhD\\FirstYearProject\\data\\df_error_socialscience.rds")

df.error.agg <- read_rds("C:\\Users\\rkm160630\\OneDrive - The University of Texas at Dallas\\Ritesh Folder\\PhD\\FirstYearProject\\data\\df_error_agg_socialscience.rds")


```



```{r}
df.error <- df.error %>% arrange(sample_size, questions)
df.error
```

```{r}
df.error.agg <- df.error.agg %>% arrange(sample_size, parameter, group)
df.error.agg
```

```{r}

df.error.plot <- df.error %>% inner_join(
  df.error.agg
) 

df.error.plot

```

```{r}

df.error.agg %>% 
  ggplot() + 
  aes(x=ratio, y=sampling_error_mean, color = group, fill = group, group = group) +
  geom_line() +
  labs(x="Student to Item Ratio") +
  facet_wrap(parameter~.)

```


```{r}

df.error %>% 
  ggplot() + 
  aes(x=ratio, y=sampling_error, fill = group) +
  geom_boxplot(alpha = 0.4) +
  labs(x="Student to Item Ratio") +
  facet_wrap(parameter~.)


```

```{r}

df.error.plot %>% 
  ggplot() + 
  aes(x=ratio, y=sampling_error, fill = group) +
  geom_violin(alpha = 0.6, trim = FALSE, color = "white") +
  geom_line(aes(y=sampling_error_mean, color = group, group = group), linetype = 1, size = 1) + 
  geom_point(aes(y=sampling_error_mean), size = 1) + 
  
  labs(x="Student to Item Ratio") +
  facet_grid(parameter~group)

```


```{r}

df.error.plot %>%
  ggplot() + 
  aes(x=ratio, y=sampling_error, fill = group) +
  geom_jitter(alpha = 0.09, width = 0.15) +
  geom_line(aes(y=sampling_error_mean, color = group, group = group), linetype = 1, size = 1) + 
  geom_point(aes(y=sampling_error_mean), size = 1) + 
  
  labs(x="Student to Item Ratio") +
  facet_grid(parameter~group) + 
  ggtitle("Sampling Error of Each Item")

```

```{r}

df.error.plot %>%
  ggplot() + 
  aes(x=ratio, y=sampling_error, fill = group) +
  geom_point(aes(color = group),alpha = 0.2, position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.2)) +
  geom_line(aes(y=sampling_error_mean, color = group, group = group), linetype = 1, size = 1) + 
  geom_point(aes(y=sampling_error_mean), size = 1) + 
  
  labs(x="Student to Item Ratio") +
  facet_grid(parameter~.) + 
  ggtitle("Sampling Error of Each Item")

```

```{r}

df.error.agg %>% select(parameter, group, sampling_error_mean, sample_size, ratio) %>% 
  spread(key="group", value = "sampling_error_mean") %>%
  
  ggplot() + 
  aes(x=`Partition 1`, y=`Partition 2`, group = 1) +
  geom_line() +
  
  labs(x="Student to Item Ratio") +
  facet_grid(.~parameter) + 
  ggtitle("Sampling Error of Each Item")

```


```{r}

df.error.plot %>% select(parameter, group, questions, sampling_error, sample_size, ratio) %>% 
  spread(key="group", value = "sampling_error") %>% arrange(sample_size) %>%
  
  
  
  ggplot() + 
  aes(x=`Partition 1`, y=`Partition 2`, color = ratio) +
  geom_point() +
  
  labs(x="Student to Item Ratio") +
  facet_grid(parameter~ratio, scales = "free") + 
  ggtitle("Sampling Error of Each Item")

```
