---
title: "CDM Pilot Study for Social Science"
output: html_notebook
---


```{r}
library(ggplot2)
library(ggpubr)
library(CDM)
library(boot)
library(tidyverse)
library(stringi)
library(stringr)
```

# Read Data
```{r}
rm(list = ls())
source('calculate_parameters.R')
options(max.print=100)


#df.X <- read_csv("..\\data\\measurement_invariance\\X.csv") %>% mutate_all(as.integer)

df.X <- read_csv("..\\data\\measurement_invariance\\Exam4Trial1_X.csv") %>% mutate_all(as.integer) %>% bind_rows(
  read_csv("..\\data\\measurement_invariance\\Exam4Trial2_X.csv") %>% mutate_all(as.integer)
) 

#df.Q <- read_csv("..\\data\\measurement_invariance\\Q.csv") %>% mutate_all(as.integer)

df.Q <- read_csv("..\\data\\measurement_invariance\\Exam4Trial1_Q.csv") %>% mutate_all(as.integer) %>% bind_rows(
  read_csv("..\\data\\measurement_invariance\\Exam4Trial2_Q.csv") %>% mutate_all(as.integer)
) %>% distinct_all()


#X = df.X %>% select(-SubjectID, -File) %>% rename_all(function(x) paste0("Q",x))
X = df.X %>% select(-SubjectID) %>% rename_all(function(x) paste0("Q",x))

Q = df.Q %>% select(-Q_UNIQUE_ID) %>% rename_all(function(x) paste0("S",x))
X <- as.data.frame(X) 
Q <- as.data.frame(Q) 

```

```{r}
X 
```




```{r }
Q
```


# Student to Item Ratio

```{r}

dim(X)[1] / dim(X)[2]

```


```{r}
#n=dim(X)[1]
#X <- X %>% sample_n(size = n, replace = FALSE)
```

```{r}
percent_na <- round((sum(is.na(X)) / (dim(X)[1] * dim(X)[2])) * 100,2)
percent_na
```

# Summary of Attempts

```{r}

summary(colSums(!is.na(X)))

```


# Student Performance


# Bootstrap Sample 

Boot requires a custom function that would return row wise stats. In case of dataframe, each row is considered as a multi-variate observation. First parameter of the custom function takes the data input and second parameter takes the importance of data given current bootstrap itestudent_question_ration. stype defines second parameter.



```{r}



#X <- as.data.frame(X) 
#Q <- as.data.frame(Q) 




#model_dina <- gdina(data =  data.ecpe$data[,-1] , q.matrix =  data.ecpe$q.matrix, maxit = 10, rule = "GDINA2")

model_dina <- din(data = X, q.matrix =  Q, progress = FALSE)
model_dina
```



# Calculate item parameters

```{r}
# Let's suffle X
#X <- X %>% sample_frac(20, replace = TRUE)
#dim(X)
#Divide X to 2 parts
#X.p1 <- X %>% head(round(dim(X)[1]/2))
#X.p2 <- X %>% tail(round(dim(X)[1]/2))


```



```{r message=FALSE, warning=FALSE}

sample_sizes <- get_sample_sizes(dim(X)[1], dim(X)[2])

colSums(!is.na(X)) 

df.t <- get_mean_sample_error(X, Q, sample_sizes[1])

df.error <- df.t[[1]]
df.error.agg <- df.t[[2]]
df.error.fit <- df.t[[3]]
df.data.sim.item <- df.t[[4]]

```


```{r message=FALSE, warning=FALSE}

for(i in 2:length(sample_sizes)) {
  
  df.t <- get_mean_sample_error(X, Q, sample_sizes[i])
  
  df.error.t <- df.t[[1]]
  df.error.agg.t <- df.t[[2]]
  df.error.fit.t <- df.t[[3]]
  df.data.sim.item.t <- df.t[[4]]
  
  df.error <- df.error %>% union(
    
    df.error.t
  )
  
  df.error.agg <- df.error.agg %>% union(
    
    df.error.agg.t
  )
  
  df.error.fit <- df.error.fit %>% union(
    
    df.error.fit.t
  )  
  
  df.data.sim.item <- df.data.sim.item %>% union(
  
  df.data.sim.item.t
  )
  
}

#debugonce(get_mean_sample_error)

```

```{r}
write_rds(df.error, "..\\data\\measurement_invariance\\df_error_socialscience.rds")

write_rds(df.error.agg, "..\\data\\measurement_invariance\\df_error_agg_socialscience.rds")

write_rds(df.error.fit, "..\\data\\measurement_invariance\\df_error_fit_socialscience.rds")

write_rds(df.data.sim.item, "..\\data\\measurement_invariance\\df_data_sim_item_socialscience.rds")

```
