---
title: "R Notebook"
output: html_notebook
---



```{r}

library(ggplot2)
library(ggpubr)
library(CDM)
library(boot)
library(tidyverse)
library(dummy)
library(stringi)
library(stringr)


```


```{r}

rm(list = ls())

x_pre <- read_csv("data\\OUTPUT.csv")

glimpse(x_pre)

```


```{r}

head(x_pre)

```

```{r}

x.gather <-x_pre %>% gather(key = "key", value = "value", -File, -SubjectID)
x.gather 
```



```{r}
x.questions <- 
  
  x.gather %>% filter(str_detect(key, "Question")) 

x.questions.dist <- x.questions %>% distinct(value) %>% drop_na() %>%  mutate(Q_UNIQUE_ID = row_number())

x.questions.dist 

```

```{r}

x.answers <- 
  
  x.gather %>% filter(!str_detect(key, "Question"))

x.answers
```


```{r}
x.questions %>% distinct(key)
```


```{r}
x.answers %>% distinct(key)
```


```{r}

x.questions.id <- x.questions %>% inner_join(x.questions.dist) %>% mutate(Q_UNIQUE_ID  = factor(Q_UNIQUE_ID)) 

x.questions.id
```


```{r}
#x.questions.id %>% mutate(var = 1) %>% select(-key)  %>% spread(key = "Q_UNIQUE_ID", value = "var")
```


```{r}

x.questions.id[c(2596, 9789),] 

```



```{r}

x.questions.id[c(1330, 3101),] 

```



```{r}

x.questions.id[c(8679, 11543),] 

```

```{r}

x.questions.id[c(1871, 6917),] 

```

```{r}

x.questions.id[c(1458, 5003),] 

```

```{r}
x.questions.id[c(3221, 6926),] 
```

```{r}

x.questions.id.filterd <- x.questions.id %>% anti_join(x.questions.id %>% group_by(File, SubjectID, value) %>% summarise(cnt = n(), question_number = paste(key, collapse = ",")) %>% filter(cnt > 1) %>% ungroup(), by = "value")


x.questions.id.filterd

```


We have the correct Questions. Now we need to add marks of answers against the questions.
```{r}

X.pre <- x.questions.id.filterd %>% mutate(id = str_split(key, " ", simplify = TRUE)[,2]) %>% 
  inner_join(
    
    x.answers %>% mutate(id = str_split(key, " ", simplify = TRUE)[,3]), by = c("File", "SubjectID", "id")
    
    ) %>% mutate(value.y = as.integer(value.y))

write_csv(X.pre, "X_Pre.csv")
X.pre
```

```{r}


X<- X.pre %>% select(-key.x, -key.y, -value.x, -id ) %>% spread(key = "Q_UNIQUE_ID", value = "value.y")

write_csv(X, "X.csv")
X
```

Let's run some test to verify X
```{r}

X %>% select(-File, -SubjectID) %>% summarise_all(sum, na.rm = TRUE)

```

```{r}

X %>% gather(key = "QuestionID", value = "Score", -File, -SubjectID)

```

```{r}

X %>% gather(key = "QuestionID", value = "Score", -File, -SubjectID) %>% filter(File == "Exam1Trial1") %>% mutate(Score = fct_explicit_na(as.character(Score))) %>% group_by(SubjectID, Score) %>% tally() %>%
  
  ggplot() + 
  aes(x=SubjectID, y=n, fill = Score) + 
  geom_col(position = position_dodge2()) + facet_wrap(Score~., scales = "free")
  

```

```{r}

X %>% gather(key = "QuestionID", value = "Score", -File, -SubjectID) %>% filter(File == "Exam1Trial1") %>% mutate(Score = fct_explicit_na(as.character(Score))) %>% filter(Score != "(Missing)") %>% group_by(SubjectID, Score) %>% tally() %>%
  
  ggplot() + 
  aes(x=SubjectID, y=n, fill = Score) + 
  geom_col(position = position_stack())
  

```

# How many times a question is asked
```{r}

X %>% gather(key = "QuestionID", value = "Score", -File, -SubjectID) %>% filter(File == "Exam1Trial1") %>% mutate(Score = fct_explicit_na(as.character(Score))) %>% filter(Score != "(Missing)") %>% group_by(QuestionID, Score) %>% tally() %>% filter(n > 4) %>%
  
  ggplot() + 
  aes(x=QuestionID, y=n, fill = Score) + 
  geom_col(position = position_stack()) + 
  stat_mean() + facet_wrap(Score~.) + coord_flip()
  

```

```{r}

X %>% gather(key = "QuestionID", value = "Score", -File, -SubjectID) %>% filter(File == "Exam1Trial1") %>% mutate(Score = fct_explicit_na(as.character(Score))) %>% group_by(SubjectID, Score) %>% tally() %>% filter(n > 4) %>% ungroup() %>%
  
  ggplot() + 
  aes(x=SubjectID, y=n, fill = Score) + 
  geom_col(position = position_stack()) + 
  stat_summary(fun.y = min, geom = "line") + 
  stat_mean() + facet_grid(Score~., scales = "free") 
  

```

# Filter questions asked in Exam I

```{r}

library(janitor)
X %>% filter(File == "Exam1Trial1") %>% remove_empty(.,which = "cols")

```

#Quantify Sparsity
```{r}


X %>% filter(File == "Exam1Trial1") %>% remove_empty(.,which = "cols") %>% 
  gather(key = "QuestionID", value = "Scores", -File, -SubjectID) %>% 
  group_by(File, SubjectID) %>%
  summarise(total_na = sum(is.na(Scores)), total = n(), total_attempted = total - total_na) %>% 
  
  ggplot() + aes(x=SubjectID, y = total_attempted) + geom_col() + geom_hline(aes(yintercept = min(total_attempted))) + geom_hline(aes(yintercept = max(total_attempted)))


```

#Question attempts for Exam1Trial1

```{r}


X %>% filter(File == "Exam1Trial1") %>% remove_empty(.,which = "cols") %>% 
  gather(key = "QuestionID", value = "Scores", -File, -SubjectID) %>% 
  group_by(File, QuestionID) %>%
  summarise(total_na = sum(is.na(Scores)), total = n(), total_attempted = total - total_na) %>% 
  
  ggplot() + aes(x=QuestionID, y = total_attempted) + geom_col() + 
  geom_hline(aes(yintercept = min(total_attempted))) + geom_hline(aes(yintercept = max(total_attempted))) + 
  coord_flip()


```

#Question attempts for All Trials

```{r}


X %>%  remove_empty(.,which = "cols") %>% 
  gather(key = "QuestionID", value = "Scores", -File, -SubjectID) %>% 
  group_by(File, QuestionID) %>%
  summarise(total_na = sum(is.na(Scores)), total = n(), total_attempted = total - total_na) %>% 
  
  ggplot() + aes(x=QuestionID, y = total_attempted) + geom_col() + 
  geom_hline(aes(yintercept = min(total_attempted))) + geom_hline(aes(yintercept = max(total_attempted))) + 
   facet_grid(.~File, scales = "free")


```

# Questions with good attempt count
```{r}


question_attempted <- X %>% remove_empty(.,which = "cols") %>% 
  gather(key = "QuestionID", value = "Scores", -File, -SubjectID) %>% 
  group_by(File, QuestionID) %>%
  summarise(total_na = sum(is.na(Scores)), total = n(), total_attempted = total - total_na)

question_attempted <- question_attempted %>% filter(total_attempted >= 8)

question_attempted

#%>% filter(QuestionID == "103")

```

Filtering out questions with lesser attempts

```{r}

X_filtered <- X %>% remove_empty(.,which = "cols") %>% 
  gather(key = "QuestionID", value = "Scores", -File, -SubjectID) %>% semi_join(question_attempted, by = c("File", "QuestionID")) %>% 
  spread(key = "QuestionID", value = "Scores")

X_filtered
```



# Take away questions answered less that 5 times per exam
```{r}
X %>% remove_empty(.,which = "cols") %>% write_csv("data\\X.csv")

X_filtered %>% remove_empty(.,which = "cols") %>% write_csv("data\\X_filtered.csv")
```

Write CSVs seperate for each trial to avoid having columns for those questions that were not asked in a trial. This will help to show the true picture of sparsity. 
```{r}

df %>%
  nest(-Rkey) %>% 
  pwalk(function(Rkey, data) write_csv(data, file.path(temp_dir, paste0(Rkey, ".csv"))))

```









